---
title: "Day06_Study_Note"
author: "Yibo Qi"
date: "2026-05-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Day06 R Learning Diary
## Today's Study Info
- Study Duration: 40 minutes
- Module: Missing value detection, data filling, sorting, column renaming

## Core Knowledge Points
1. `is.na()` detect missing values in dataset.
2. `na.omit()` directly delete all rows contain NA.
3. Use `mean(..., na.rm=TRUE)` to calculate mean ignoring missing data.
4. `order()` sort dataset in ascending or descending order.
5. `colnames()` modify variable column names quickly.
6. Logical filter can remove unreasonable outlier data.

## Runable R Code Today
```{r}
# ==== Day06 Data Cleaning & Sorting ====
# Construct simulated psychological data with missing values
sub_id <- 1:7
sex <- c("M","F","M","F","NA","M","F")
edu <- c(16,18,15,17,19,NA,16)
sleep_score <- c(45,52,38,60,49,55,NA)

# Combine data frames
cli_data <- data.frame(sub_id,sex,edu,sleep_score)

# 1. Check NA values
is.na(cli_data) # Missing positions judged by logic
sum(is.na(cli_data)) # Count the total number of missing values
colSums(is.na(cli_data)) # Count missing values by column

# 2. Delete rows with NA
clean_data_omit <- na.omit(cli_data)

# 3. Fill NA with mean value
cli_data$sleep_score[is.na(cli_data$sleep_score)] <- mean(cli_data$sleep_score, na.rm = TRUE)

# 4. Sort data
# Sort by sleep score in ascending order
data_asc <- cli_data[order(cli_data$sleep_score), ]
# Sort by sleep score in descending order
data_desc <- cli_data[order(-cli_data$sleep_score), ]

# 5. Rename columns
colnames(cli_data) <- c("ID","Gender","Education","Sleep_score")

# 6. Simple elimination of outliers
valid_data <- cli_data[cli_data$Sleep_Score >= 30 & cli_data$Sleep_Score <= 70, ]
```

