---
title: "Day03_Study_Note"
author: "Yibo Qi"
date: "2026-05-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Day03 Learning Diary
## Today's Study Info
- Study Duration: 40 minutes
- Module: Factor variable, logical subsetting, basic statistics

## Core Knowledge Points
1. 'factor()' converts character vector into categorical variable for grouping.
2. 'levels()' checks category labels of a factor.
3. Use logical condition '> < >= <= == &' to subset data.
4. Square bracket '[]' can filter elements by condition.
5. Basic stats: 'mean()', 'sd()', 'min()', 'max()' for descriptive analysis.

## Runable R Code Today
```{r}
# ==== Day03 Factor & Logical Subset ====

# 1. Character vector
group <- c("Control", "Clinical", "Control", "Clinical", "Clinical")

# 2. Convert to Factor
group_factor <- factor(group)

# 3. Check Factor Level
group_factor
levels(group_factor)

# 4. Filter Numeric Vectors
score <- c(25, 33, 41, 28, 35)

# 5. Logical Subset
score > 30
score[score > 30] # Filter scores greater than 30

# 6. Filter scores greater than 30
score[score >= 28 & score <= 38]
 
# 7. Group Filtering by Factors
score[group_factor == "Clinical"]
score[group_factor == "Control"]

# 8. Basic Statistical Functions
mean(score)
sd(score)
min(score)
max(score)
```

