---
title: "Day04_Study_Note"
author: "Yibo Qi"
date: "2026-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Day04_Study_Note
## Today's Study Info
- Study Duration: 40 minutes
- Module: Data fame creation, data view, row & column extraction, data filter

## Core Knowledge Points
1. 'data.frame()' combine different vectors into standard research dataset.
2. Use '$' to extract single column variable quickly.
3. 'head()' check top rows, 'str()'inspect data structure.
4. '[row, column]' to locate specific data position.
5. Filter whole dataset by logical condition for subgroup analysis.
6. Can add new calculated column directly to data frame.

## Runable R Code Today
```{r}
# ==== Day04 Data Frame ====

# 1.Construct simulated data for psychological experiments
id <- 1:6 # Subject ID
gender <- c("F", "M", "F", "M", "F", "M") # Gender
age <- c(22,25,23,24,26,21) # Age
dep_score <- c(18,27,15,32,20,29) # Depression Score
anx_score <- c(12,22,10,25,14,23) # Anxiety Score

# 2.Combine into a data frame
psy_data <- data.frame(id, gender, age, dep_score, anx_score)

# 3.View data as a whole
psy_data
head(psy_data) # View the first few rows
str(psy_data) # View data structure

# 4.Extract data by column
psy_data$age
psy_data$dep_score

# 5.Retrieve values by rows and columns
psy_data[2, ] # Extract all data from the second row
psy_data[ ,4] # Extract all data from the 4th column
psy_data[3,5] # Single value in the 3rd row and 5th column

# 6.Filter table data by conditions
male_data <- psy_data[psy_data$gender=="M",] # Screen male participants
high_dep <- psy_data[psy_data$dep_score > 25, ] # Screen out people with depression scores higher than 25 points

# 7.Add a new column of variables
psy_data$total_score <- psy_data$dep_score + psy_data$anx_score
```

