---
title: "Day05_Study_Note"
author: "Yibo Qi"
date: "2026-05-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Day05 R Learning Diary
## Today's Study Info
- Study Duration: 40 minutes
- Module: Package installation, library load, working directory, CSV & Excel data import

## Core Knowledge Points
1. 'install.packages()' install new functional packages.
2. 'library()' activate installed packages before use.
3. 'getwd()' check current file path, 'setwd()' set target folder.
4. 'readr' package is stable for CSV file reading an writing.
5. 'redxl' package supports direct reading Excel spreadsheet data.
6. Built-in dataset 'iris' is widely used for statistical pratice.

## Runable R Code Today
```{r}
# ==== Day05 Package & External Data Import ====

# 1. Check working directory
getwd()

# 2. Set working directory
# setwd("Your local folder path")

# 3. Install packages
install.packages("readr") # Efficient Reading and Writing of CSV Files
install.packages("readxl") # Read Excel files

# 4. Load packages
library(readr)
library(readxl)

# 5. Practice with built-in datasets
data(iris)
head(iris)
str(iris)

# 6. Simulate exporting data as CSV
psy_data <- iris
write_csv(psy_data, "Psychology_Score_Data.csv")

# 7. Read CSV files
csv_data <- read_csv("Psychology_Score_Data.csv")

# 8. Read Excel spreadsheet Import Excel 
# excel_data <- read_excel("Your_Data.xlsx")

```

